The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2014-07-03 article.tex
author spelling error
work on fingerprint table

% Load packages
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
\usepackage{amssymb}
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\urlstyle{rm}
\usepackage{cite}

@@

\setlength{\topmargin}{0.0cm}
\setlength{\textheight}{21.5cm}
\setlength{\oddsidemargin}{0cm} 
\setlength{\textwidth}{16.5cm}
\setlength{\columnsep}{0.6cm}

@@

\author{
  Egon L Willighagen$^{1}$% // FIXED FIRST AUTHOR
  \email{Egon L Willighagen - egon.willighagen@maastrichtuniversity.nl}
\and
  John May$^2$% // FIXED SECOND AUTHOR
  \email{John May - COMPLETE@ebi.ac.uk}
\and
  Jonathan Alversson$^3$%
  \email{Jonathan Alversson - COMPLETE}
\and
  Arvid Berg$^3$%
  \email{Arvid Berg - COMPLETE}
\and
  Nina Jeliazkova$^4$%
  \email{Nina Jeliakvova - COMPLETE}
\and
  Dazhi Jiao$^5$%
  \email{Dazhi Jiao - COMPLETE}
\and
  Syed Asad Rahman$^6$%
  \email{Syed Asad Rahman - COMPLETE}
\and
  Mark Rijnbeek$^2$%
  \email{Mark Rijnbeek - COMPLETE}
\and
  Miguel Rojas Cherto$^7$%
  \email{Miguel Rojas Cherto - COMPLETE}
\and
  Ola Spjuth$^3$%
  \email{Ola Spjuth - ola.spjuth@farmbio.uu.se}
\and
  Gilleain Torrance$^5$%
  \email{Gilleain Torrance - COMPLETE}
\and
  Rajarshi Guha$^{8}$% // FIXED ONE BUT LAST AUTHOR
  \email{Rajarshi Guha - COMPLETE}
\and
  Christoph Steinbeck$^{2}$% // FIXED LAST AUTHOR
  \email{Christoph Steinbeck - steinbeck@ebi.ac.uk}
}

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
  \subsection*{Table 1 - The molecular fingerprints in CDK}
    \par
    \mbox{
    \begin{tabular}{lcclrc}
                             & Bit version  & Count version & CDK version & Default Size & References \\
  \cline{2-6}\noalign{\smallskip}
  EStateFingerprinter        & $\checkmark$ &               & 1.2.0       & $79$         & \cite{Hall1995}\\
  ExtendedFingerprinter      & $\checkmark$ &               & 1.0         &              & \\
  Fingerprinter              & $\checkmark$ &               & 1.0         &              & \\
  GraphOnlyFingerprinter     & $\checkmark$ &               & 1.0         &              & \\
  HybridizationFingerprinter & $\checkmark$ &               & 1.4.0       &              & \\
  KlekotaRothFingerprinter   & $\checkmark$ &               & 1.4.6       & $4\,860$     & \cite{Klekota2008}\\
  LingoFingerprinter         & $\checkmark$ &               & 1.6.0 ?     &              & \\
  MACCSFingerprinter         & $\checkmark$ &               & 1.2.0       &              & \\
  PubchemFingerprinter       & $\checkmark$ &               & 1.4.0       &              & \\
  ShortestPathFingerprinter  & $\checkmark$ &               & 1.6.0 ?     &              & \\
  SignatureFingerprinter     & $\checkmark$ & $\checkmark$  & 1.6.0 ?     & $2^{32}$     & [pending] \\
  SubstructureFingerprinter  & $\checkmark$ &               & 1.0         &              & \\
    \end{tabular}}

>>>>

% Load packages
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
\usepackage{amssymb}
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\urlstyle{rm}
\usepackage{cite}
\usepackage[table]{xcolor}
\usepackage{booktabs}

@@

\setlength{\topmargin}{0.0cm}
\setlength{\textheight}{21.5cm}
\setlength{\oddsidemargin}{0cm} 
\setlength{\textwidth}{16.5cm}
\setlength{\columnsep}{0.6cm}
\definecolor{lightgray}{gray}{0.9}

@@

\author{
  Egon L Willighagen$^{1}$% // FIXED FIRST AUTHOR
  \email{Egon L Willighagen - egon.willighagen@maastrichtuniversity.nl}
\and
  John May$^2$% // FIXED SECOND AUTHOR
  \email{John May - COMPLETE@ebi.ac.uk}
\and
  Jonathan Alvarsson$^3$%
  \email{Jonathan Alvarsson - COMPLETE}
\and
  Arvid Berg$^3$%
  \email{Arvid Berg - COMPLETE}
\and
  Nina Jeliazkova$^4$%
  \email{Nina Jeliakvova - COMPLETE}
\and
  Dazhi Jiao$^5$%
  \email{Dazhi Jiao - COMPLETE}
\and
  Syed Asad Rahman$^6$%
  \email{Syed Asad Rahman - COMPLETE}
\and
  Mark Rijnbeek$^2$%
  \email{Mark Rijnbeek - COMPLETE}
\and
  Miguel Rojas Cherto$^7$%
  \email{Miguel Rojas Cherto - COMPLETE}
\and
  Ola Spjuth$^3$%
  \email{Ola Spjuth - ola.spjuth@farmbio.uu.se}
\and
  Gilleain Torrance$^5$%
  \email{Gilleain Torrance - COMPLETE}
\and
  Rajarshi Guha$^{8}$% // FIXED ONE BUT LAST AUTHOR
  \email{Rajarshi Guha - COMPLETE}
\and
  Christoph Steinbeck$^{2}$% // FIXED LAST AUTHOR
  \email{Christoph Steinbeck - steinbeck@ebi.ac.uk}
}

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
  \subsection*{Table 1 - The molecular fingerprints in CDK}
    \rowcolors{1}{}{lightgray}
    \par
    \mbox{
    \begin{tabular}{lcclrc}
    \toprule
                             & Bit version  & Count version & CDK version & Default Size & References \\
  EStateFingerprinter        & $\checkmark$ &               & 1.2.0       & $79$         & \cite{Hall1995}\\
  ExtendedFingerprinter      & $\checkmark$ &               & 1.0         &              & \\
  Fingerprinter              & $\checkmark$ &               & 1.0         &              & \\
  GraphOnlyFingerprinter     & $\checkmark$ &               & 1.0         &              & \\
  HybridizationFingerprinter & $\checkmark$ &               & 1.4.0       &              & \\
  KlekotaRothFingerprinter   & $\checkmark$ &               & 1.4.6       & $4\,860$     & \cite{Klekota2008}\\
  LingoFingerprinter         & $\checkmark$ &               & 1.6.0 ?     &              & \\
  MACCSFingerprinter         & $\checkmark$ &               & 1.2.0       &              & \\
  PubchemFingerprinter       & $\checkmark$ &               & 1.4.0       &              & \\
  ShortestPathFingerprinter  & $\checkmark$ &               & 1.6.0 ?     &              & \\
  SignatureFingerprinter     & $\checkmark$ & $\checkmark$  & 1.6.0 ?     & $2^{32}$     & [pending] \\
  SubstructureFingerprinter  & $\checkmark$ &               & 1.0         &              & \\
  CirkularFingerprinter      & $\checkmark$ & ?             & ?           & ?            & [pending?] \\
  \bottomrule
    \end{tabular}}
